19Q1

### 2019-05-09 19Q1.Rmd
update CRISPR plots and Rmd

    # Get all G2P gene-cell line combinations
    grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = g2p_genes)
    data <-  merge(filt, grid, by = "Cell_line", all.y = TRUE)
    print("Merged grid.")
    # Merge metadata
    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.y = TRUE)
    ## Add columns for G2P drug-gene and drug-gene-lineage sorting
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_druggenes, "Yes", "No")
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
    print("Merged metadata.")
  }
  if(database == "CRISPR") {
    print(paste0("Processing ", database, " data."))
    # Melt CRISPR dataset for merging
    data <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
    # Get all G2P gene-cell line combinations
    data <-  filter(data, Gene %in% g2p_genes)
    # Merge cell line metadata
    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.y = TRUE)
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
    print("Merged metadata.")
  }

  # Merge mutation calls
  data <- unfactorize(data)
  data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
  data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
  ## Identify point mutations
  # data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
  ## Summarize number of mutant and Wildtype cell lines
  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
  ## Merge test results back into full dataset, which restores information lost in the summarization
  data <- merge(data_muts_summ, data, by = "Gene")
  print("Merged mutation calls.")

@@

# Summarize number of mutant and Wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
## Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
crispr_data$Mutation_Status <- factor(crispr_data$Mutation_Status)
## Add Color column
crispr_data$Color <- ifelse(crispr_data$Mutation_Status == 0, "thistle", "darkorchid")
crispr_data$Color <- factor(crispr_data$Color)

@@

futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
             filename = "./plots/manuscript/all_venn_ccls.png",
             output = TRUE, imagetype = "png",
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1,
             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             # cat.dist = c(0.06, 0.06, 0.035),
             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))

venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
             filename = "./plots/manuscript/drug_venn_ccls.png",
             output = TRUE, imagetype = "png",
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1.4,
             category.names = c("CCLE", "CTRP", "GDSC"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             cat.dist = c(0.06, 0.06, 0.035),
             fill = c("springgreen4", "steelblue4", "turquoise4"))
```

@@

```{r histology_dists, fig.height=4.5, fig.width=4}
drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
  geom_bar(stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
  labs(y = "Count")
dev.off()
```

@@

@@

```{r wilcoxon_tests, eval=FALSE}
crispr_ptmuts <- unfactorize(crispr_ptmuts)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")

@@

```{r crispr_mut_gene_plot, fig.height=4, fig.width=8}
crispr_signif_gene$Gene <- factor(crispr_signif_gene$Gene, levels = g2p_genes)
crispr_ptmuts$Gene <- factor(crispr_ptmuts$Gene, levels = g2p_genes)

crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts) +
  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
  geom_jitter(aes(x = Mutation_Status, y = Score, color = Mutation_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Mutation_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  theme(legend.position = "top", legend.direction = "horizontal") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "CERES Score")
crispr_gene_mut_plot

ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
```

@@

crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts) +
  facet_wrap(~ Primary.Disease, nrow = 6, scales = "free_x") +
  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  geom_point(aes(x = Gene, y = Score, color = Mutation_Status), alpha = 0.5, size = 0.6) +
  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.6, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1, size = 3) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  ylab("CERES Score") +
  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut"))
crispr_gene_lin_plot

ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
```

@@

Spearman correlations for gene expression and copy number:
```{r crispr_spear_calc, warning=FALSE}
crispr_spear_ge <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
crispr_spear_cn <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
```

@@

Create CRISPR two-column, KRAS-inset plot for CN and GE:
```{r crispr_spear_plot, fig.height=6, fig.width=12}
spearman_KRAS <- rbind(filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))

crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = TPM, y = Score)) +
  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
  labs(x = "KRAS Gene Expression (TPM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))

crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = CN, y = Score)) +
  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
  labs(x = expression("KRAS Copy Number"~(log[2]-ratio)), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))

>>>>

    # Get all G2P gene-cell line combinations
    grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = g2p_genes)
    data <-  merge(filt, grid, by = "Cell_line", all.y = TRUE)
    print("Merged grid.")
    # Merge metadata
    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.y = TRUE)
    ## Add columns for G2P drug-gene and drug-gene-lineage sorting
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_druggenes, "Yes", "No")
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
    data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
  }
  if(database == "CRISPR") {
    print(paste0("Processing ", database, " data."))
    # Melt CRISPR dataset for merging
    data <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
    # Get all G2P gene-cell line combinations
    data <-  filter(data, Gene %in% g2p_genes)
    # Merge cell line metadata
    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.y = TRUE)
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
    data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
  }

  ## Summarize number of mutant and Wildtype cell lines
  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
  ## Merge test results back into full dataset, which restores information lost in the summarization
  data <- merge(data_muts_summ, data, by = "Gene")
  print("Merged mutation calls.")

@@

# Summarize number of mutant and Wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
## Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
crispr_data$Mutation_Status <- factor(crispr_data$Mutation_Status)

@@

futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
             filename = "./plots/manuscript/all_venn_ccls.png",
             output = TRUE, imagetype = "png",
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1,
             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             # cat.dist = c(0.06, 0.06, 0.035),
             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
             filename = "./plots/manuscript/drug_venn_ccls.png",
             output = TRUE, imagetype = "png",
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1.4,
             category.names = c("CCLE", "CTRP", "GDSC"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             cat.dist = c(0.06, 0.06, 0.035),
             fill = c("springgreen4", "steelblue4", "turquoise4"))
```

@@

```{r histology_dists, fig.height=4.5, fig.width=4}
drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
# png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
  geom_bar(stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
  labs(y = "Count")
# dev.off()
```

@@

## AUC heatmap

```{r}
ccle_auc_grid <- dcast(filter(ccle_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
ctrp_auc_grid <- dcast(filter(ctrp_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
gdsc_auc_grid <- dcast(filter(gdsc_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)

ccle_auc_ht <- Heatmap(ccle_auc_grid,
                       name = "AUC",
                       show_column_names = FALSE, 
                       column_title = "CCLE",
                       column_title_side = "top")
ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
                       name = "AUC",
                       show_column_names = FALSE, 
                       column_title = "CTRP",
                       column_title_side = "top")
gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
                       name = "AUC",
                       show_column_names = FALSE, 
                       column_title = "GDSC",
                       column_title_side = "top")

draw(ccle_auc_ht)
draw(ctrp_auc_ht)
draw(gdsc_auc_ht)
```

@@

```{r wilcoxon_tests, eval=FALSE}
crispr_ptmuts <- unfactorize(crispr_ptmuts)
# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_gene.rds")
crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")

@@

```{r crispr_mut_gene_plot, fig.height=4, fig.width=8}
crispr_signif_gene$Gene <- factor(crispr_signif_gene$Gene, levels = g2p_genes)
crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
crispr_ptmuts_filt$Gene <- factor(crispr_ptmuts_filt$Gene, levels = g2p_genes)
crispr_ptmuts_filt$Mutation_Status <- as.character(crispr_ptmuts_filt$Mutation_Status)

crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts_filt) +
  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
  geom_jitter(aes(x = Mutation_Status, y = Score, color = Mutation_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Mutation_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  theme(legend.position = "top", legend.direction = "horizontal") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "CERES Score")
# crispr_gene_mut_plot

# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
```

@@

crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts_filt) +
  facet_wrap(~ Primary.Disease, nrow = 6, scales = "free_x") +
  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  geom_point(aes(x = Gene, y = Score, color = Mutation_Status), alpha = 0.5, size = 0.6) +
  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.6, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1, size = 3) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  ylab("CERES Score") +
  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut"))
# crispr_gene_lin_plot

# ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
```

@@

Spearman correlations for gene expression and copy number:
```{r crispr_spear_calc, warning=FALSE}
crispr_spear_ge <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
crispr_spear_cn <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
```

@@

Create CRISPR two-column, KRAS-inset plot for CN and GE:
```{r crispr_spear_plot, fig.height=6, fig.width=12}
spearman_KRAS <- rbind(filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))

crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = TPM, y = Score)) +
  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
  labs(x = expression("KRAS Gene Expression"~(log[2](TPM))), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))

crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = CN, y = Score)) +
  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
  labs(x = expression("KRAS Copy Number"~(log[2]-ratio)), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
